Converging High-Throughput and High-Performance Computing: A Case Study

### 2017-03-28 overall.tex
Eliminate subsection on reliability, second paragraph and figure

\mtnote{Figure summarizing job performance on Titan analogous to those produced
with NGE, as discussed in F2F meeting at Rutgers?}

% ----------------------------------------------------------------------------
\subsection{Reliability of PanDA Broker and Detector Simulations on Titan}
\label{ssec:reliability}

@@

Figure~\ref{fig:failures-titan} shows a breakdown of the type of failures
recorded by the PanDA Brokers between January 2016 and February 2017. The
initial preponderance of unknown failures was progressively addressed by a more
accurate failure model, specifically tailored to the PanDA Broker and Titan.
Figure~\ref{fig:failures-titan} also shows the progressive improvement of the
broker's reliability: In Februrary 2017, errors related to input files and
initialization were almost eliminated and execution errors were comparable to
those recorded in January 2017 even if almost twice as many simulations were
performed (Figure~\ref{fig:backfill-utilization}). The increased amount of
unknown failure in February indicates that furter work is needed to improve the
PanDA Broker failure model.

\begin{figure}[htp]
    \includegraphics[clip,width=\columnwidth]{figures/failures_titan.pdf}
    \caption{PanDA Broker failures during the experiment time window. Failures
    were recorded with 52 exit codes, here aggregated into 6 categories. The
    number of failures should be compared to the number of simulations executed
    in each month as plotted in Figure~\ref{fig:backfill-utilization}.
    Improvements in the failure model of PanDA Broker shows a decrease in
    unknown failure and a the progressive addressing of other categories of
    failure.}
\label{fig:failures-titan}
\end{figure}

>>>>

% \mtnote{Figure summarizing job performance on Titan analogous to those
% produced with NGE, as discussed in F2F meeting at Rutgers?}

% ----------------------------------------------------------------------------
% \subsection{Reliability of PanDA Broker and Detector Simulations on Titan}
% \label{ssec:reliability}

@@

% Figure~\ref{fig:failures-titan} shows a breakdown of the type of failures
% recorded by the PanDA Brokers between January 2016 and February 2017. The
% initial preponderance of unknown failures was progressively addressed by a
% more accurate failure model, specifically tailored to the PanDA Broker and
% Titan. Figure~\ref{fig:failures-titan} also shows the progressive improvement
% of the broker's reliability: In Februrary 2017, errors related to input files
% and initialization were almost eliminated and execution errors were comparable
% to those recorded in January 2017 even if almost twice as many simulations
% were performed (Figure~\ref{fig:backfill-utilization}). The increased amount
% of unknown failure in February indicates that furter work is needed to improve
% the PanDA Broker failure model.

% \begin{figure}[htp]
%     \includegraphics[clip,width=\columnwidth]{figures/failures_titan.pdf}
    % \caption{PanDA Broker failures during the experiment time window. Failures
    % were recorded with 52 exit codes, here aggregated into 6 categories. The
    % number of failures should be compared to the number of simulations
    % executed in each month as plotted in
    % Figure~\ref{fig:backfill-utilization}. Improvements in the failure model
    % of PanDA Broker shows a decrease in unknown failure and a the progressive
    % addressing of other categories of failure.}
% \label{fig:failures-titan}
% \end{figure}
